A full approximation storage multilevel method \\ for nonlinear variational inequalities

### 2023-06-12 paper/fascd.tex
visualize a V-cycle; see comments before fig:imagesvcycle regarding generation

\usepackage{tikz}
\usetikzlibrary{decorations.pathreplacing}

@@

>>>>

\usepackage{tikz}
\usetikzlibrary{decorations.pathreplacing}
\usetikzlibrary{graphs}

@@

% figures in the following visualization were generated using branch elbueler/simplefigs
% of git@bitbucket.org:pefarrell/fascd.git, and the following commands:
%   cd examples/
%   python3 plap1d.py -figures -fascd_max_it 2 -fascd_cycle_type multiplicative -mcoarse 2
\begin{figure}[ht]
\begin{center}
\input{tikz/imagesvcycle.tex}
\end{center}
\caption{Visualization of one iteration of \textsc{FASCD-VCYCLE} (Algorithm \ref{alg:fascd}) in the case of Example FIXME with $p=1.5$ and $J=3$.  Level iterates and solutions ($w^j$, $y^j$, $z^j$) are lines while obstacles and defect constraints ($\underline{\gamma}^j$, $\underline{\phi}^j\le 0$, $\underline{\chi}^j\le 0$) are strong dots.  The coarsest mesh $\mathcal{T}^0$ has two elements.}
\label{fig:imagesvcycle}
\end{figure}
